### 2015-11-06 Paper/paper.tex
Added ACM template

\documentclass{sigchi}

% Use this command to override the default ACM copyright statement
% (e.g. for preprints).  Consult the conference website for the
% camera-ready copyright statement.

%% EXAMPLE BEGIN -- HOW TO OVERRIDE THE DEFAULT COPYRIGHT STRIP -- (July 22, 2013 - Paul Baumann)
\toappear{One does not simply copy this document.}
%% EXAMPLE END -- HOW TO OVERRIDE THE DEFAULT COPYRIGHT STRIP -- (July 22, 2013 - Paul Baumann)

% Arabic page numbers for submission.  Remove this line to eliminate
% page numbers for the camera ready copy
% \pagenumbering{arabic}

% Load basic packages
\usepackage{balance}  % to better equalize the last page
\usepackage{graphics} % for EPS, load graphicx instead 
\usepackage[T1]{fontenc}
\usepackage{txfonts}
\usepackage{mathptmx}
\usepackage[pdftex]{hyperref}
\usepackage{color}
\usepackage{booktabs}
\usepackage{textcomp}
% Some optional stuff you might like/need.
\usepackage{microtype} % Improved Tracking and Kerning
% \usepackage[all]{hypcap}  % Fixes bug in hyperref caption linking
\usepackage{ccicons}  % Cite your images correctly!
\usepackage[utf8]{inputenc} % for a UTF8 editor only

% If you want to use todo notes, marginpars etc. during creation of your draft document, you
% have to enable the "chi_draft" option for the document class. To do this, change the very first
% line to: "\documentclass[chi_draft]{sigchi}". You can then place todo notes by using the "\todo{...}"
% command. Make sure to disable the draft option again before submitting your final document.
\usepackage{todonotes}

% Paper metadata (use plain text, for PDF inclusion and later
% re-using, if desired).  Use \emtpyauthor when submitting for review
% so you remain anonymous.
\def\plaintitle{University of the Philippines Los Baños Online Student Information System}
\def\plainauthor{Jan Keith Darunday, Ferriel Lisandro Melarpis, Toni-Jan Keith Monserrat, and Reginald Neil Recario}
\def\emptyauthor{}
\def\plainkeywords{Authors' choice; of terms; separated; by
  semicolons; include commas, within terms only; required.}
\def\plaingeneralterms{Documentation, Standardization}

% llt: Define a global style for URLs, rather that the default one
\makeatletter
\def\url@leostyle{%
  \@ifundefined{selectfont}{
    \def\UrlFont{\sf}
  }{
    \def\UrlFont{\small\bf\ttfamily}
  }}
\makeatother
\urlstyle{leo}

% To make various LaTeX processors do the right thing with page size.
\def\pprw{8.5in}
\def\pprh{11in}
\special{papersize=\pprw,\pprh}
\setlength{\paperwidth}{\pprw}
\setlength{\paperheight}{\pprh}
\setlength{\pdfpagewidth}{\pprw}
\setlength{\pdfpageheight}{\pprh}

% Make sure hyperref comes last of your loaded packages, to give it a
% fighting chance of not being over-written, since its job is to
% redefine many LaTeX commands.
\definecolor{linkColor}{RGB}{6,125,233}
\hypersetup{%
  pdftitle={\plaintitle},
% Use \plainauthor for final version.
%  pdfauthor={\plainauthor},
  pdfauthor={\emptyauthor},
  pdfkeywords={\plainkeywords},
  bookmarksnumbered,
  pdfstartview={FitH},
  colorlinks,
  citecolor=black,
  filecolor=black,
  linkcolor=black,
  urlcolor=linkColor,
  breaklinks=true,
}

% create a shortcut to typeset table headings
% \newcommand\tabhead[1]{\small\textbf{#1}}

% End of preamble. Here it comes the document.
\begin{document}

\title{\plaintitle}

%Jan Keith Darunday, Ferriel Lisandro Melarpis, Toni-Jan Keith Monserrat, and Reginald Neil Recario
\numberofauthors{4}
\author{%
  \alignauthor{Jan Keith Darunday\\
    \affaddr{Los Ba\~{n}os, Philippines}\\
    \email{jcdarunday@up.edu.ph}}\\
  \alignauthor{Ferriel Lisandro Melarpis\\
    \affaddr{Los Ba\~{n}os, Philippines}\\
    \email{fbmelarpis@up.edu.ph}}\\
  \alignauthor{Toni-Jan Keith Monserrat\\
    \affaddr{Los Ba\~{n}os, Philippines}\\
    \email{tonijanmonserrat@gmail.com}}\\
%   \alignauthor{Reginald Neil Recario\\
%     \affaddr{Los Ba\~{n}os, Philippines}\\
%     \email{rcrecario@up.edu.ph}}\\
}

\maketitle

\begin{abstract}
  UPDATED---\today. This sample paper describes the formatting
  requirements for SIGCHI conference proceedings, and offers
  recommendations on writing for the worldwide SIGCHI
  readership. Please review this document even if you have submitted
  to SIGCHI conferences before, as some format details have changed
  relative to previous years. Abstracts should be about 150 words and
  are required.
\end{abstract}

\category{K.3.2}{Computing Milieux}{COMPUTERS AND EDUCATION }{Computer and Information Science Education }

\keywords{\plainkeywords}

\section{Introduction}

This format is to be used for submissions that are published in the
conference proceedings. We wish to give this volume a consistent,
high-quality appearance. We therefore ask that authors follow some
simple guidelines. You should format your paper exactly like this
document. The easiest way to do this is to replace the content with
your own material.  This document describes how to prepare your
submissions using \LaTeX.

\section{Another Section}
On each page your material should fit within a rectangle of 7 $\times$
9.15 inches (18 $\times$ 23.2 cm), centered on a US Letter page (8.5
$\times$ 11 inches), beginning 0.85 inches (1.9 cm) from the top of
the page, with a 0.3 inches (0.85 cm) space between two 3.35 inches
(8.4 cm) columns. Right margins should be justified, not
ragged. Please be sure your document and PDF are US letter and not A4. \cite{acm_categories,cavender:writing,CHINOSAUR:venue,psy:gangnam}

% REFERENCES FORMAT
% References must be the same font size as other body text.
\bibliographystyle{sigchi}
\bibliography{paper}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2015-11-07 Paper/paper.tex
Added introduction

@@
 %% EXAMPLE BEGIN -- HOW TO OVERRIDE THE DEFAULT COPYRIGHT STRIP -- (July 22, 2013 - Paul Baumann)
-\toappear{One does not simply copy this document.}
+%\toappear{One does not simply copy this document.}
 %% EXAMPLE END -- HOW TO OVERRIDE THE DEFAULT COPYRIGHT STRIP -- (July 22, 2013 - Paul Baumann)
@@
 
-\begin{abstract}
-  UPDATED---\today. This sample paper describes the formatting
-  requirements for SIGCHI conference proceedings, and offers
-  recommendations on writing for the worldwide SIGCHI
-  readership. Please review this document even if you have submitted
-  to SIGCHI conferences before, as some format details have changed
-  relative to previous years. Abstracts should be about 150 words and
-  are required.
-\end{abstract}
-
-\category{K.3.2}{Computing Milieux}{COMPUTERS AND EDUCATION }{Computer and Information Science Education }
-
-\keywords{\plainkeywords}
+% \begin{abstract}
+% \end{abstract}
+% 
+% \category{K.3.2}{Computing Milieux}{COMPUTERS AND EDUCATION }{Computer and Information Science Education }
+% 
+\keywords{student; information; registration; enrollment}
 
@@
 
-This format is to be used for submissions that are published in the
-conference proceedings. We wish to give this volume a consistent,
-high-quality appearance. We therefore ask that authors follow some
-simple guidelines. You should format your paper exactly like this
-document. The easiest way to do this is to replace the content with
-your own material.  This document describes how to prepare your
-submissions using \LaTeX.
+In campuses under the University of the Philippines (UP) System, students have 
+more freedom to choose the subjects that they want to enroll in compared to other
+universities. UP employs the Revitalized General Education Program (RGEP) that
+requires students to take General Education (GE) courses. They have the ability to
+choose which of these courses they would like to enlist in.
+These GE courses are courses that allow students from any degree program to enroll
+unlike major courses that are only available to certain degree programs. The
+ability to choose one’s subjects implied that almost all students will need to
+manually fill-up their list of courses to enroll to before the beginning of 
+every semester. Moreover, courses are divided into sections each of which have 
+a limited number of slots for students that it can accommodate. This meant that 
+not only will the students need to manually check for conflicts in their 
+schedules, they will also need to check if the course that they want to enlist 
+in still has slots remaining.
 
-\section{Another Section}
-On each page your material should fit within a rectangle of 7 $\times$
-9.15 inches (18 $\times$ 23.2 cm), centered on a US Letter page (8.5
-$\times$ 11 inches), beginning 0.85 inches (1.9 cm) from the top of
-the page, with a 0.3 inches (0.85 cm) space between two 3.35 inches
-(8.4 cm) columns. Right margins should be justified, not
-ragged. Please be sure your document and PDF are US letter and not A4. \cite{acm_categories,cavender:writing,CHINOSAUR:venue,psy:gangnam}
+The complexity of this process along with the increasing availability of Internet access to
+the public incited the development of computerized Online Registration Systems (ORS). These
+systems allowed the enlistment, cancellation, and swapping of slots for courses over the Internet.
+These systems also did the checking of conflicting subjects and availability of slots automatically
+so that students will not need to do them manually.
+In the University of the Philippines Los Baños (UPLB), the Online Registration System that
+is used as of the writing of this paper is called SystemOne. This system has undergone various
+revisions and improvements as old technology become deprecated by new ones and problems
+encountered in previous versions are fixed. The most recent one identifies itself as the third
+version and is code-named “Decaf”. However, this system did not prove to be efficient enough
+for the student population of UPLB despite several rewrites and revisions.
 
-% REFERENCES FORMAT
-% References must be the same font size as other body text.
-\bibliographystyle{sigchi}
-\bibliography{paper}
+As a solution, we propose that there needs to be a complete rewrite of 
+the system. Because SystemOne is originally written in the PHP programming 
+language which has been known to be slow, using a faster programming language 
+would be an improvement. SystemOne also has its database connection as its 
+bottleneck but it tries to solve this by using memcache as a caching system. 
+However, this wasn't efficient enough as queries executed by the backend is too
+dynamic which makes the results hard to cache. In order to alleviate the effects
+of this bottlneck, we propose that three differnt database/storage systems will
+be used. One will be a RAM-based storage system with high-speed read/write that
+does not need to support queries, another would be a database system that 
+supports fast queries and uses a non-volatile memory storage, the last one would
+be a full-fledged relational database system that will be used for persistent
+storage.
+
+% % REFERENCES FORMAT
+% % References must be the same font size as other body text.
+% \bibliographystyle{sigchi}
+% \bibliography{paper}
+
+\cleardoublepage
 

### 2015-11-07 Paper/paper.tex
Added command that removes copyright section
Added draft for RRL

@@
 
+% remove copyright
+\makeatletter
+\def\@copyrightspace{\relax}
+\makeatother
+
 % End of preamble. Here it comes the document.
@@
 
+\section{Related Work}
+
+There is a limited number of papers that specifically discuss SystemOne. These papers
+mostly focus on the various modules that provide different kinds of functionality for SystemOne
+and the features to be created rather than the speed and feasibility of the use of the system.
+Suayan (1997) developed one of the first registration systems used in UPLB called the
+UPLB RegisNet. This system was designed to automate the pre-enlistment of subjects for
+students.
+
+Meanwhile, the UPLB Academic Information System was created and had support for
+modularity. Through its modularity, various modules were created for it. Cruz (2001) created a
+Subjects module that gave it the ability to add, edit, and delete subjects from a list of subjects and
+Almodiel (2001) developed a module that allowed teachers to add, search, and view the grades of
+a student in their respective classes. Enrique (2001) then developed a Schedule of Classes
+module that was responsible for managing and viewing the schedule of a subject, a room, or a
+teacher.
+
+The UPLB University Data Resource Network is another system used in UPLB. It was
+created in 2003 and was also designed to be able to support modules. Gimotea (2003) was the
+one who developed the Curricular, Degree Course, Class Schedules, and Room Assignment
+Module which gave it functionalities similar to those that registration systems have like the
+manipulation of schedules and rooms for classes and courses.
+After a few years, Javier, et al. (2005) developed the first version of UPLB’s Online
+Registration System called SystemOne. This system was also extensible through modularity. In
+this version, SystemOne used the Java programming language for implementing the Enlistor and
+Registrar module, PHP 5 for the Department module and MySQL as the Database Management
+System (DBMS).
+
+Because SystemOne was designed to be extensible through its support for modules, various
+modules for it has been developed around the same time as the development of original
+SystemOne. Curativo, et al. (2005) developed a web service module so that SystemOne can be
+accessible using a web browser. Before that, users had to use the Java application for SystemOne
+for them to be able to access it. Cardenas, et al. (2005) also developed another module called the
+Data Manager Interface (DMI) which was responsible for allowing SystemOne to access a
+Database Management System (DBMS) and converting data given by the Office of the
+University Registrar through the REGIST system into a database that can be understood by
+SystemOne. Both of these modules also used the Java programming language and supported the
+MySQL DBMS.
+
+In the year 2010, the development of the UPLB SystemOne V2 began. This version also
+used the Java programming language and the MySQL DBMS and was also modular. However,
+the difference of this new system from the previous system was that even the core functions were
+divided into modules and was developed separately.
+
+Payoyo (2010) developed the Announcement, Registrar and Observer Module for
+SystemOne V2 which allowed support for announcement and gave representatives from the
+registrar an interface to manage the courses to be offered among other things. Granada (2010)
+developed the Subject Planner and Student’s Checklist which gave students the ability to view
+their checklist and plan their schedule of subjects.
+
+At the same time, Guevarra (2010) developed a Mobile Bluetooth Interface for Nokia 60
+Series Smartphones using Symbian C++. This allowed users of the Nokia 60 Series Smartphones
+to access SystemOne on their smartphones.
+
+In 2012, the third and current version of SystemOne was developed by the SystemOne
+Development Team. This system, unlike the previous versions that used Java, used the PHP
+programming language along with the MySQL DBMS. Like the second version, this system
+supports modules and its core functions are also implemented as modules.
+
+Unfortunately, it is now a known fact that Java is rather slow compared to the alternatives.
+Jelovic (n.d.) stated in one of his online articles that “anybody that has ever used a non-trivial
+Java program or has programmed in Java knows that Java is slower than native programs written
+in C++”. This is just one among the number of criticisms that Java receives when it comes to its
+speed. Despite this, Java is known to be easy to use and was designed to be good for
+network-based applications.
+
+Another programming language used in the implementations of SystemOne is the PHP
+programming language. This programming language is also known to be slow when it comes to
+large-scale web applications. What more is that the flavor of PHP that was used in the third
+version called Suhosin is known to be a bit slower than than the original PHP.
+
+There was one study that focused on the speed and response time of SystemOne. Crespo
+(2014) wrote a study entitled “Comparing the Response and Rendering Time of PHP-based
+against Javascript-based SystemOne”. This study did a comparison on how much faster or slower
+SystemOne would be had it been implemented in Javascript using the NodeJS interpreter. Her
+study detailed the performance of her own Javascript-based implementation against the
+PHP-based implementation. The results of her study showed that the Javascript-based
+implementation yielded a 52 percent increase in overall speed.
+
+These results seem to be very promising considering the fact that NodeJS is known to not be
+able to take full advantage of a server computer that has multiple cores yet. This shows that
+SystemOne could have been faster if the right choices were made.
+These studies show a history of Online Registration Systems used in UPLB. It can be seen in
+the papers and articles cited that the use of the best and fastest technology has not really been
+given consideration.
+
+\section{Methodology}
+
+\subsection{Database}
+
+The system will utilized three database systems. These database systems are as
+follows:
+\begin{enumerate}
+\item High-Speed Read and Write Storage System - This will be shared across all
+clusters. This needs to high speed because it will used to store information
+that change very fast and is read repeatedly such as the number of slots for
+every subject.
+
+\item High-Speed Read and Medium-Speed Write Relational Database System - Also 
+shared across all clusters, this will contain data and information that are not
+changed often but are read a repeatedly a lot such as the information for subjects
+and their dependencies, user accounts, and recommended courses.
+
+\item Persistent Relational Database System - This will be used as the permanent
+storage for all data. The other two storage and database systems will synchronize
+to this database at specific intervals.
+\end{enumerate}
+
+\subsection{Backend}
+
+The backend will be a server that serves a Representational State Transfer (REST)
+Application Programming Interface (API) through the Hypertext Transfer Protocol
+(HTTP). The system's backend shall have multithreading support. A thread will be 
+spawned for every successful HTTP connection. This thread will handle its own
+associated connection and wait for a command before processing it and giving a 
+reply. If a command is not received or completed after a specified amount of
+time, a timeout will occur and the connection will be dropped along with its
+corresponding thread being deallocated from the memory.
+
+\subsubsection{Conflict Checking}
+
+Every time a modification or addition is done on a student's schedule, the 
+backend will check for conflicts before executing the specified action. 
+To do this, a bitwise AND will be done on the current user's schedule and the
+schedule of the subject to be inserted. If the resulting value is not 0 then
+an error reply will be sent.
+
+\subsection{Frontend}
+
 % % REFERENCES FORMAT

### 2015-11-07 Paper/paper.tex
Revert "Added command that removes copyright section"
This reverts commit 7eb45fabde1d1b48bf19850251c3627e7921a853.
Added draft for RRL

@@
 
-\section{Methodology}
-
-\subsection{Database}
-
-The system will utilized three database systems. These database systems are as
-follows:
-\begin{enumerate}
-\item High-Speed Read and Write Storage System - This will be shared across all
-clusters. This needs to high speed because it will used to store information
-that change very fast and is read repeatedly such as the number of slots for
-every subject.
-
-\item High-Speed Read and Medium-Speed Write Relational Database System - Also 
-shared across all clusters, this will contain data and information that are not
-changed often but are read a repeatedly a lot such as the information for subjects
-and their dependencies, user accounts, and recommended courses.
-
-\item Persistent Relational Database System - This will be used as the permanent
-storage for all data. The other two storage and database systems will synchronize
-to this database at specific intervals.
-\end{enumerate}
-
-\subsection{Backend}
-
-The backend will be a server that serves a Representational State Transfer (REST)
-Application Programming Interface (API) through the Hypertext Transfer Protocol
-(HTTP). The system's backend shall have multithreading support. A thread will be 
-spawned for every successful HTTP connection. This thread will handle its own
-associated connection and wait for a command before processing it and giving a 
-reply. If a command is not received or completed after a specified amount of
-time, a timeout will occur and the connection will be dropped along with its
-corresponding thread being deallocated from the memory.
-
-\subsubsection{Conflict Checking}
-
-Every time a modification or addition is done on a student's schedule, the 
-backend will check for conflicts before executing the specified action. 
-To do this, a bitwise AND will be done on the current user's schedule and the
-schedule of the subject to be inserted. If the resulting value is not 0 then
-an error reply will be sent.
-
-\subsection{Frontend}
-
 % % REFERENCES FORMAT

### 2015-11-07 Paper/paper.tex
Added draft for Methodology

--- 2015-11-07 Paper/paper.tex
@@
 
+\subsubsection{Cross-Site HTTP Requests}
+
+The system will be designed to support HTTP Requests from specific domains
+where the frontend code will be stored. This is to be able to outsource the load
+added by frontend data being served as it will take a significant amount of
+networking bandwidth to serve the images and scripts included. This will also
+allow the frontend to have heavier images and scripts without affecting the 
+performance of the main server.
+
 \subsection{Frontend}
+
+The frontend will be a static web application that fires REST requests to the
+server. The Javascript Object Notation (JSON) will be used to specify parameters
+for commands that require sending non-anonymous data while a normal GET request
+can be used for reading data. The frontend will also have an enlistment queue
+where the user can setup which subjects he/she would like to enlist and then
+send them as a batch to the server. This would lessen the number of connections
+that the server will receive lessening the number of threads running in the 
+backend.
 

### 2015-11-07 Paper/paper.tex
Removed \cleardoublepage command
Removed some parts of the RRL to shorten it a bit and be closer to specifications

@@
 
-The UPLB University Data Resource Network is another system used in UPLB. It was
-created in 2003 and was also designed to be able to support modules. Gimotea (2003) was the
-one who developed the Curricular, Degree Course, Class Schedules, and Room Assignment
-Module which gave it functionalities similar to those that registration systems have like the
-manipulation of schedules and rooms for classes and courses.
 After a few years, Javier, et al. (2005) developed the first version of UPLB’s Online
@@
 
-Because SystemOne was designed to be extensible through its support for modules, various
-modules for it has been developed around the same time as the development of original
-SystemOne. Curativo, et al. (2005) developed a web service module so that SystemOne can be
-accessible using a web browser. Before that, users had to use the Java application for SystemOne
-for them to be able to access it. Cardenas, et al. (2005) also developed another module called the
-Data Manager Interface (DMI) which was responsible for allowing SystemOne to access a
-Database Management System (DBMS) and converting data given by the Office of the
-University Registrar through the REGIST system into a database that can be understood by
-SystemOne. Both of these modules also used the Java programming language and supported the
-MySQL DBMS.
-
-In the year 2010, the development of the UPLB SystemOne V2 began. This version also
+In 2010, the development of the UPLB SystemOne V2 began. This version also
 used the Java programming language and the MySQL DBMS and was also modular. However,
@@
 divided into modules and was developed separately.
-
-Payoyo (2010) developed the Announcement, Registrar and Observer Module for
-SystemOne V2 which allowed support for announcement and gave representatives from the
-registrar an interface to manage the courses to be offered among other things. Granada (2010)
-developed the Subject Planner and Student’s Checklist which gave students the ability to view
-their checklist and plan their schedule of subjects.
-
-At the same time, Guevarra (2010) developed a Mobile Bluetooth Interface for Nokia 60
-Series Smartphones using Symbian C++. This allowed users of the Nokia 60 Series Smartphones
-to access SystemOne on their smartphones.
 
@@
 supports modules and its core functions are also implemented as modules.
-
-Unfortunately, it is now a known fact that Java is rather slow compared to the alternatives.
-Jelovic (n.d.) stated in one of his online articles that “anybody that has ever used a non-trivial
-Java program or has programmed in Java knows that Java is slower than native programs written
-in C++”. This is just one among the number of criticisms that Java receives when it comes to its
-speed. Despite this, Java is known to be easy to use and was designed to be good for
-network-based applications.
-
-Another programming language used in the implementations of SystemOne is the PHP
-programming language. This programming language is also known to be slow when it comes to
-large-scale web applications. What more is that the flavor of PHP that was used in the third
-version called Suhosin is known to be a bit slower than than the original PHP.
 
@@
 The system will be designed to support HTTP Requests from specific domains
-where the frontend code will be stored. This is to be able to outsource the load
-added by frontend data being served as it will take a significant amount of
-networking bandwidth to serve the images and scripts included. This will also
-allow the frontend to have heavier images and scripts without affecting the 
-performance of the main server.
+where the frontend code will be stored through the Access-Control-Allow-Origin header. 
+This is to be able to outsource the load added by frontend data being served as 
+it will take a significant amount of networking bandwidth to serve the images and
+scripts included. This will also allow the frontend to have heavier images and 
+scripts without affecting the performance of the main server.
 
@@
 The frontend will be a static web application that fires REST requests to the
-server. The Javascript Object Notation (JSON) will be used to specify parameters
+backend server. The Javascript Object Notation (JSON) will be used to specify parameters
 for commands that require sending non-anonymous data while a normal GET request
-can be used for reading data. The frontend will also have an enlistment queue
+will be used for reading anonymous data. The frontend will also have an enlistment queue
 where the user can setup which subjects he/she would like to enlist and then
@@
 backend.
+
+The design for the frontend will try to follow Google's Material Design 
+Specification although not strictly. Along with this, it shall support mobile
+platforms by implementing Responsive Design.
 
@@
 
-\cleardoublepage
+%\cleardoublepage
 

### 2015-11-07 Paper/paper.tex
Added partial Evaluation section

@@
 
+%TODO: Should be 1/2
+\subsection{Evaluation}
+
+The system shall be evaluated by its stability, efficiency, ease of use, and
+integration.
+
+Its stability will be evaluated by running a fuzzer software on the different
+commands that the backend server accepts. If the fuzzer finds strings that 
+causes the backend to crash, show an error, or produce the wrong output then the
+system fails the stability test. If this happens, the errors shall be fixed and
+the system will again undergo the stability evaluation.
+
+The system's efficiency will be evaluated by running benchmarks on the system.
+Information such as requests per second, time per request, and transfer rate
+of each function will be collected. The system will also be tested if can 
+handle medium and heavy workloads by using load testing tools and services.
+These tests will use combinations of the different functions at ratios expected
+during actual use of the system.
+
+The system's ease of use will be evaluated through a survey along with additional
+criteria about other aspects of the system.
+The survey will be done with at least 500 respondents that will test the system
+and rate it under the following criteria:
+\begin{enumerate}
+ \item the ability of the user-interface to be understandable without a manual;
+ \item the way how buttons in the user-interface are positioned;
+ \item the animations embedded into the user-interface
+ \item the responsiveness of the system; and
+ \item the additional features of the system.
+\end{enumerate}
+
 % % REFERENCES FORMAT

### 2015-11-07 Paper/paper.tex
Added references on paper and bibtex file

@@
 Suayan (1997) developed one of the first registration systems used in UPLB called the
-UPLB RegisNet. This system was designed to automate the pre-enlistment of subjects for
+UPLB RegisNet \cite{suayan}. This system was designed to automate the pre-enlistment of subjects for
 students.
@@
 modularity. Through its modularity, various modules were created for it. Cruz (2001) created a
-Subjects module that gave it the ability to add, edit, and delete subjects from a list of subjects and
+Subjects module that gave it the ability to add, edit, and delete subjects from a list of subjects \cite{cruz} and
 Almodiel (2001) developed a module that allowed teachers to add, search, and view the grades of
-a student in their respective classes. Enrique (2001) then developed a Schedule of Classes
+a student in their respective classes \cite{almodiel}. Enrique (2001) then developed a Schedule of Classes
 module that was responsible for managing and viewing the schedule of a subject, a room, or a
-teacher.
+teacher \cite{enrique}.
 
 After a few years, Javier, et al. (2005) developed the first version of UPLB’s Online
-Registration System called SystemOne. This system was also extensible through modularity. In
+Registration System called SystemOne \cite{javier}. This system was also extensible through modularity. In
 this version, SystemOne used the Java programming language for implementing the Enlistor and
@@
 (2014) wrote a study entitled “Comparing the Response and Rendering Time of PHP-based
-against Javascript-based SystemOne”. This study did a comparison on how much faster or slower
+against Javascript-based SystemOne” \cite{crespo}. This study did a comparison on how much faster or slower
 SystemOne would be had it been implemented in Javascript using the NodeJS interpreter. Her
@@
 
-% % REFERENCES FORMAT
-% % References must be the same font size as other body text.
-% \bibliographystyle{sigchi}
-% \bibliography{paper}
+% REFERENCES FORMAT
+% References must be the same font size as other body text.
+\bibliographystyle{sigchi}
+\bibliography{paper}
 

### 2015-11-08 Paper/paper.tex
Converted Evaluation into a Section
Added draft for Timeline

@@
 %TODO: Should be 1/2
-\subsection{Evaluation}
+\section{Evaluation}
 
@@
 
+\section{Timeline}
+\begin{center}
+    \begin{tabular}{ | l | p{5cm} |}
+    \hline
+      Date & Activity \\ \hline
+      Day 0-7 & Planning of System Framework and Database Structures \\ \hline
+      Day 8-14 & Implementation of Basic Backend Functions Without Conflict Checking \\ \hline
+      Day 15-30 & Implementation of Conflict Checking and Integration with Backend \\ \hline
+      Day 31-45 & Development of Static Web Application Interface \\ \hline
+      Day 46-60 & Implementation of Advanced Features \\ \hline
+      Day 61-68 & Stress Testing and Fuzzing \\ \hline
+      Day 69-76 & Adjustments from the Results of Stress Testing and Fuzzing \\ \hline
+      Day 77-81 & Alpha Test of Test Users \\ \hline
+      Day 82-96 & Adjustments from the Results of Alpha Test \\ \hline
+      Day 97-103 & Beta Release \\ \hline
+    \end{tabular}
+\end{center}
+
 % REFERENCES FORMAT

### 2016-05-17 Server/src/handler.rs
Updated TODO

@@ -21,12 +21,12 @@ use crypto::blake2b::Blake2b;
 use crypto::digest::Digest;
 
 // TODO:
-// Waitlist +
-// Authentication (Sessions)
-// Roles
+// Waitlist DONE
+// Authentication (Sessions)  DONE
+// Roles DONE (partial)
 // TODO_AFTER:
 // Loading of schedule of subjects
-// Server-side conflict checking for each time period
+// Server-side conflict checking for each time period DONE
 
 fn get_db_connection(req: &mut Request) -> r2d2::PooledConnection<r2d2_redis::RedisConnectionManager>{
     req.get::<Read<RedisPool>>().unwrap().get().unwrap()
@@ -41,7 +41,6 @@ impl Enlisted{
             Ok(hashmap) => hashmap,
             Err(_) => return Ok(Response::with((status::BadRequest)))
         };
-
 
         let session = query.get("session").unwrap().get(0).unwrap();
 
@@ -249,7 +248,7 @@ impl Student{
 
         let session = query.get("session").unwrap().get(0).unwrap().clone();
 
-        let result: HashMap<String, String> = scripts["student_profile"].arg(session).invoke(redis_connection).unwrap();
+        let result: HashMap<String, String> = scripts["student_profile"].arg(session    ).invoke(redis_connection).unwrap();
 
         Ok(Response::with((status::Ok, format!("{{ \"result\":0, \"data\":{:?} }}", result))))
     }

### 2016-05-17 Server/src/handler.rs
Implemented subject importer

@@ -12,6 +12,7 @@ use router::Router;
 use urlencoded::UrlEncodedQuery;
 
 use persistent::Read;
+use std::io::Read as StdRead;
 
 use database::RedisPool;
 use scripts::Scripts;
@@ -19,6 +20,10 @@ use scripts::Scripts;
 use uuid::Uuid;
 use crypto::blake2b::Blake2b;
 use crypto::digest::Digest;
+
+use redis::Commands;
+
+use rustc_serialize::json::Json;
 
 // TODO:
 // Waitlist DONE
@@ -288,16 +293,78 @@ impl Subject{
         let subject = query.get("subject").unwrap().get(0).unwrap().clone();
         let section = query.get("section").unwrap().get(0).unwrap().clone();
         let max_slots = query.get("max_slots").unwrap().get(0).unwrap().clone();
-        //let subject = query.get("session").unwrap().get(0).unwrap().clone();
+        let schedule = query.get("schedule").unwrap().get(0).unwrap().clone();
         let lecture = match query.get("lecture") {
             Some(s) => s.get(0).unwrap().clone(),
             None => "".to_string()
         };
 
         let result: i32 = scripts["admin_subject_add"]
-        .arg(session).arg(subject).arg(section).arg(max_slots).arg(lecture)
+        .arg(session).arg(subject).arg(section).arg(max_slots).arg(schedule).arg(lecture)
         .invoke(redis_connection).unwrap();
 
         Ok(Response::with((status::Ok, format!("\"result\" :{:?}", result))))
+    }
+}
+
+pub struct Admin;
+impl Admin{
+    pub fn import_subjects(req: &mut Request) -> IronResult<Response> {
+        let redis_connection = &get_db_connection(req) as &redis::Connection;
+        let scripts = req.get::<Read<Scripts>>().unwrap();
+        let session = match req.get::<UrlEncodedQuery>() {
+            Ok(hashmap) => hashmap.get("session").unwrap().get(0).unwrap().clone(),
+            Err(_) => return Ok(Response::with((status::BadRequest)))
+        };
+        let role: i32 = redis_connection.hget("sessions:".to_string() + &session.clone(), "role").unwrap();
+
+        if role != 9 {
+            return Ok(Response::with((status::BadRequest)))
+        }
+
+        let mut body = String::new();
+        req.body.read_to_string(&mut body).unwrap();
+        let decoded = Json::from_str(&body);
+        let data = match decoded {
[…]

### 2016-05-17 Server/src/main.rs

@@ -14,6 +14,8 @@ extern crate redis;
 // extern crate r2d2_mysql
 // extern crate mysql_simple
 
+extern crate rustc_serialize;
+
 // Auth crates
 extern crate uuid;
 extern crate crypto;
@@ -77,6 +79,11 @@ fn main(){
         put "/create" => handler::Subject::put
     );
 
+    let admin_router = router!(
+        post "/import_subjects" => handler::Admin::import_subjects,
+        post "/import_students" => handler::Admin::import_students
+    );
+
     println!("Connecting to database..");
     let redis_db = database::redis_connect("redis://127.0.0.1", 512);
     println!("Done.");
@@ -89,6 +96,7 @@ fn main(){
     mount.mount("/student/", student_router);
     mount.mount("/auth/", auth_router);
     mount.mount("/subject/", subject_router);
+    mount.mount("/admin/", admin_router);
 
     let mut chain = Chain::new(mount);
     chain.link(Read::<RedisPool>::both(redis_db));

### 2016-05-17 Server/src/handler.rs
Implement units and purity for subject importer

@@ -331,19 +331,26 @@ impl Admin{
         };
 
         //println!("{:?}", );
+
         let mut results = vec![];
         let subject_data = data.as_object().unwrap();
         for (subject, value) in subject_data.get("subjects").unwrap().as_object().unwrap().iter() {
             for (section, value) in value.as_object().unwrap().iter(){
                 let section_object = value.as_object().unwrap();
-                let slots = match section_object.get("slots").unwrap(){
-                    &Json::String(ref slots) => slots.clone(),
-                    _ => "0".to_string()
+                let slots = match section_object.get("slots") {
+                    Some(slots) => match slots {
+                        &Json::U64(ref slots) => slots.clone(),
+                        _ => 0
+                    },
+                    None => {println!("{} {:?}", subject, section_object); 0}
                 };
 
-                let schedule = match section_object.get("schedule_code").unwrap(){
-                    &Json::String(ref slots) => slots.clone(),
-                    _ => "|||||".to_string()
+                let schedule = match section_object.get("schedule_code") {
+                    Some(schedule) => match schedule {
+                        &Json::String(ref schedule) => schedule.clone(),
+                        _ => "|||||".to_string()
+                    },
+                    None => {println!("{:?}", section_object); "|||||".to_string()}
                 };
 
                 let lecture = match section_object.get("lecture") {
@@ -354,17 +361,44 @@ impl Admin{
                     None => "".to_string()
                 };
 
+                let units = match section_object.get("units") {
+                    Some(units) => match units {
+                        &Json::U64(ref units) => units.clone(),
+                        _ => 0
+                    },
+                    None => 0
+                };
+
+                let is_pure = match section_object.get("pure") {
+                    Some(is_pure) => match is_pure {
+                        &Json::U64(ref is_pure) => is_pure.clone(),
+                        _ => 1
+                    },
+                    None => 1
+                };
+
                 let result: i32 = scripts["admin_subject_add"]
-                .arg(session.clone()).arg(subject.clone()).arg(section.clone()).arg(slots).arg(schedule).arg(lecture)
+                .arg(session.clone())
+                .arg(subject.clone())
+                .arg(section.clone())
+                .arg(slots)
+                .arg(schedule)
+                .arg(units)
+                .arg(lecture)
+                .arg(is_pure)
                 .invoke(redis_connection).unwrap();
[…]

### 2016-05-17 Client/scripts/config.js
Change client prototype

@@ -1,6 +1,0 @@
-'use strict';
-
-var config = {
-  client_url: '',
-  server_url: 'http://localhost:3000'
-}

### 2016-05-17 Client/scripts/heartland.js

@@ -1,105 +1,0 @@
-'use strict';
-
-function HeartLand(mainui) {
-  this.user = null;
-  this.ajax = new Ajax();
-  this.ui = mainui;
-
-  this.ui.bind(this);
-  var $ = this;
-  var classes = $_CLASS('menuChoice');
-  for (var i = 0; i < classes.length; i++) {
-    classes[i].onclick = function() {
-      // $.updateSection(this, this.id);
-    }
-  }
-
-  if (cookie.get('sessionID') != null) {
-    var user = cookie.get('user');
-    $_ID('login').style.display = 'none';
-    setTimeout(function() {
-      $_ID('login').style.display = 'block';
-    }, 300);
-    this.ui.login(JSON.parse(user));
-    // this.updateSection($_ID('home'), 'home');
-  }
-
-  window.addEventListener('storage', function(e) {
-    if (e.key === 'loggedin') {
-      if (e.newValue === 'false') {
-        $.logout();
-      } else {
-        var user = cookie.get('user');
-        $.ui.login(JSON.parse(user));
-        // $.updateSection($_ID('home'), 'home');
-      }
-    }
-  }, false);
-}
-
-HeartLand.prototype.login = function(username, password) {
-  var $ = this;
-  var url = config.server_url + '/auth/login';
-  var params = '?username=' + username + '&password=' + password;
-  this.ajax.request('post', url + params, function(r) {
-    var res;
-
-    try {
-      console.log(r)
-      res = JSON.parse(r);
-      console.log(res)
-    } catch (e) {
-      alert('The server has responded with invalid data.');
-    }
-
-    switch (res.result) {
-      case 0:
-        $.user = {
-          'name': username,
-          'units': 18,
-          'icon': './images/account-circle-icon.png'
-        };
-        $.ui.login($.user);
-        cookie.set('user', JSON.stringify($.user));
-        cookie.set('sessionID', res.key);
-        localStorage.loggedin = 'true';
-        break;
-      case -1: // wrong password
-        return alert('Error: Incorrect password.');
-        break;
-      case -2: // user does not exist
-        return alert('Error: User does not exist.');
-        break;
-    }
-  });
-}
-
-HeartLand.prototype.logout = function() {
-  var $ = this;
-  var url = config.server_url + '/auth/logout';
-  var params = '?session=' + cookie.get('sessionID');
-
-  this.ajax.request('delete', url + params, function(r) {
[…]

### 2016-05-17 Client/scripts/main.js

@@ -1,3 +1,0 @@
-'use strict';
-
-window.onload = function () { return new HeartLand(new UserInterface(this)); };

### 2016-05-17 HeartlandTester/lib/schedule-renderer.js

@@ -1,0 +1,273 @@
+		var sourceColors = [
+			"#F44336",
+			"#3F51B5",
+			"#4CAF50",
+			"#FF9800",
+			"#E91E63",
+			"#2196F3",
+			"#8BC34A",
+			"#FF5722"
+
+			// 		"#673AB7",
+			// 		"#009688",
+			// 		"#FFC107",
+			// 		"#607D8B",
+			// 		"#9C27B0",
+			// 		"#00BCD4",
+			// 		"#9E9E9E",
+			// 		"#FFEB3B",
+			// 		"#795548"
+
+			// 			"#00008b",
+			// 			"#008b8b",
+			// 			"#a9a9a9",
+			// 			"#006400",
+			// 			"#bdb76b",
+			// 			"#8b008b",
+			// 			"#556b2f",
+			// 			"#ff8c00",
+			// 			"#9932cc",
+			// 			"#8b0000",
+			// 			"#e9967a",
+			// 			"#9400d3"
+		];
+
+		var colors = [];
+		var subjectColors = {};
+
+		function fillRectangle(context, offsetX, offsetY, sizeX, sizeY, color) {
+			context.beginPath();
+			context.rect(offsetX, offsetY, sizeX, sizeY);
+			context.fillStyle = color;
+			context.fill();
+			context.closePath();
+		}
+
+		function drawLine(context, beginX, beginY, endX, endY, color, width) {
+			context.beginPath();
+			context.moveTo(beginX, beginY);
+			context.lineTo(endX, endY);
+			context.strokeStyle = color;
+			context.lineWidth = width;
+			context.stroke();
+			context.closePath();
+		}
+
+		function drawText(context, beginX, beginY, text, style, color) {
+			context.beginPath();
+			context.font = style;
+			context.fillStyle = color;
+			context.fillText(text, beginX, beginY);
+			context.closePath();
+		}
+
+		function drawTextCentered(context, beginX, beginY, sizeX, sizeY, text, size,
+			font, color, weight) {
+			context.beginPath();
+			context.font = weight + " " + size + "px " + font;
+			context.fillStyle = color;
+			context.fillText(text, beginX + (sizeX / 2 - context.measureText(text).width /
+				2), beginY + (sizeY / 2) + (size / 2));
+			context.closePath();
+		}
+
+		function drawTextOffsetCentered(context, beginX, beginY, sizeX, sizeY,
+			lineOffset, text, size, font, color, weight) {
+			context.beginPath();
[…]

### 2016-05-17 HeartlandTester/main.js

@@ -1,0 +1,157 @@
+var subjects = {}
+
+$.ajax({
+  url: 'subjects.json',
+  success: function(data) {
+    console.log(data)
+    subjects = data.subjects
+  }
+})
+
+function login() {
+  $.ajax({
+    type: 'POST',
+    url: 'http://localhost:3000/auth/login?username=' + $("#username").val() + '&password=' + $("#password").val(),
+    success: function(data) {
+      var res = JSON.parse(data);
+      if (res.key) {
+        $("#session").val(res.key);
+        Materialize.toast("Successfully logged in.", 1000);
+      } else {
+        Materialize.toast("Failed to logged in.", 1000);
+      }
+      console.log(res)
+    }
+  })
+  return false;
+}
+
+function logout() {
+  $.ajax({
+    type: 'POST',
+    url: 'http://localhost:3000/auth/logout?session=' + $("#session").val(),
+    success: function(data) {
+      var res = JSON.parse(data);
+      if (res.result == 0) {
+        $("#session").val('-');
+        Materialize.toast("Successfully logged out.", 1000);
+      } else {
+        Materialize.toast("Failed to logged out.", 1000);
+      }
+
+    }
+  })
+  return false
+}
+
+function get_profile() {
+  $.ajax({
+    type: 'GET',
+    url: 'http://localhost:3000/student/profile?session=' + $("#session").val(),
+    success: function(data) {
+      var res = JSON.parse(data);
+      $("#student_profile").html(
+        `<td>${res.data.student_number}</td>
+        <td>${res.data.first_name}</td>
+        <td>${res.data.middle_name}</td>
+        <td>${res.data.last_name}</td>
+        <td>${res.data.curriculum}</td>
+        <td>${res.data.standing}</td>
+        <td>${res.data.total_units}</td>
+        <td>${res.data.max_units}</td>`
+      )
+      console.log(res)
+    }
+  })
+  return false
+}
+
+function get_schedule() {
+  $.ajax({
+    type: 'GET',
+    url: 'http://localhost:3000/student/schedule?session=' + $("#session").val(),
+    success: function(data) {
+      var res = JSON.parse(data);
+      var html = ''
+
+      var c = initializeSched($("#schedule")[0]);
+
+      for (subject in res.data) {
+        var section = res.data[subject]
+        let subdata = subjects[subject][section]
[…]

### 2016-05-17 Server/src/handler.rs
Implement unit limiting

@@ -398,7 +398,26 @@ impl Admin{
             Ok(Response::with((status::Ok, format!("\"result\" :0"))))
     }
 
-    pub fn create_admin(_: &mut Request) -> IronResult<Response> {
-            Ok(Response::with((status::Ok, format!("\"result\" :0"))))
+    pub fn create_admin(req: &mut Request) -> IronResult<Response> {
+        let redis_connection = &get_db_connection(req) as &redis::Connection;
+        let scripts = req.get::<Read<Scripts>>().unwrap();
+        let query = match req.get::<UrlEncodedQuery>() {
+            Ok(hashmap) => hashmap,
+            Err(_) => return Ok(Response::with((status::BadRequest)))
+        };
+        let username = query.get("username").unwrap().get(0).unwrap().clone();
+        let password = {
+            let password = query.get("password").unwrap().get(0).unwrap();
+            let mut blake = Blake2b::new(32);
+            blake.input_str(&password);
+            blake.result_str()
+        };
+        let res: i32 = match query.get("session") {
+            Some(session_list) =>
+                scripts["admin_create"].arg(session_list.get(0).unwrap().clone()).arg(username).arg(password).invoke(redis_connection).unwrap(),
+            None =>
+                scripts["auth_register"].arg(username).arg(password).arg(9).invoke(redis_connection).unwrap()
+        };
+        Ok(Response::with((status::Ok, format!("{{ \"result\" :{} }}", res))))
     }
 }

### 2016-05-17 Server/src/main.rs

@@ -81,7 +81,8 @@ fn main(){
 
     let admin_router = router!(
         post "/import_subjects" => handler::Admin::import_subjects,
-        post "/import_students" => handler::Admin::import_students
+        post "/import_students" => handler::Admin::import_students,
+        post "/create" => handler::Admin::create_admin,
     );
 
     println!("Connecting to database..");

### 2016-05-17 Server/src/scripts.rs

@@ -30,7 +30,7 @@ pub fn get_scripts() -> HashMap<String, Script>{
         "student_profile",
         "subject_waitlist_count", "subject_slots",
         "auth_login", "auth_logout", "auth_register",
-        "admin_subject_add", "admin_student_add"
+        "admin_subject_add", "admin_student_add", "admin_create"
      ];
 
     for file in filenames {

### 2016-05-20 Paper/sp2-paper.tex
Update paper

--- 2015-11-08 Paper/paper.tex
@@
-\documentclass{sigchi}
+\documentclass[draft]{sigchi}
 
@@
 \usepackage[T1]{fontenc}
+\usepackage{placeins}
 \usepackage{txfonts}
@@
 \usepackage{textcomp}
+\usepackage{pgfplots}
 % Some optional stuff you might like/need.
@@
 % so you remain anonymous.
-\def\plaintitle{University of the Philippines Los Baños Online Student Information System}
+\def\plaintitle{Flash Crowd Online Student Enrollment System}
 \def\plainauthor{Jan Keith Darunday, Ferriel Lisandro Melarpis, Toni-Jan Keith Monserrat, and Reginald Neil Recario}
@@
     \email{tonijanmonserrat@gmail.com}}\\
-%   \alignauthor{Reginald Neil Recario\\
-%     \affaddr{Los Ba\~{n}os, Philippines}\\
-%     \email{rcrecario@up.edu.ph}}\\
+  \alignauthor{Reginald Neil Recario\\
+    \affaddr{Los Ba\~{n}os, Philippines}\\
+    \email{rcrecario@up.edu.ph}}\\
 }
@@
 
-In campuses under the University of the Philippines (UP) System, students have 
-more freedom to choose the subjects that they want to enroll in compared to other
-universities. UP employs the Revitalized General Education Program (RGEP) that
-requires students to take General Education (GE) courses. They have the ability to
-choose which of these courses they would like to enlist in.
-These GE courses are courses that allow students from any degree program to enroll
+In academic institutions with large student populations such as campuses under
+the University of the Philippines (UP) System, the implementation of an online registration
+system for students is considered to be one of the biggest challenges as the system needs
+to be capable of handling the surge of network connections from the whole student population
+during the online registration period. Some of these systems were created by students studying 
+in their respective universities and some of the others were created by software development
+companies paid by the university. However, many of these systems failed
+to address need of the institution that it serves due to issues like lack of budget, lack of development time,
+use of wrong or outdated technologies, and lack of consultation of what the users actually need.
+
+This research paper will use the enrollment system and online registration system in
+the University of the Philippines as a context.
+
+In the UP System, students are free to enlist into General Education (GE)
+courses. These GE courses are courses that allow students from any degree program to enlist into
 unlike major courses that are only available to certain degree programs. The
@@
 for the student population of UPLB despite several rewrites and revisions.
+This paper seeks to improve open this kind of online registration by fixing the problems encountered
+by SystemOne as a basis.
 
-As a solution, we propose that there needs to be a complete rewrite of 
-the system. Because SystemOne is originally written in the PHP programming 
+Because SystemOne is originally written in the PHP programming 
 language which has been known to be slow, using a faster programming language 
@@
 However, this wasn't efficient enough as queries executed by the backend is too
-dynamic which makes the results hard to cache. In order to alleviate the effects
-of this bottlneck, we propose that three differnt database/storage systems will
-be used. One will be a RAM-based storage system with high-speed read/write that
-does not need to support queries, another would be a database system that 
-supports fast queries and uses a non-volatile memory storage, the last one would
-be a full-fledged relational database system that will be used for persistent
-storage.
+dynamic which makes the results hard to cache. There are also lots of workarounds
+that try to solve the race conditions that occur. Our system will try to solve this
+by choosing a more feasible database system for sudden surges of requests.
 
@@
 
-The system will utilized three database systems. These database systems are as
-follows:
-\begin{enumerate}
-\item High-Speed Read and Write Storage System - This will be shared across all
-clusters. This needs to high speed because it will used to store information
-that change very fast and is read repeatedly such as the number of slots for
-every subject.
+As an information system, the speed of the system depends heavily on the speed
+of the database management system since most of the requests that it handles
+do modification of data. Because of this, Redis was chosen as it is a database
+management system that has low runtime overhead and very fast request-serving
+speeds with benchmarks showing hundreds of thousands of requests per second for
+atomic functions.
 
-\item High-Speed Read and Medium-Speed Write Relational Database System - Also 
-shared across all clusters, this will contain data and information that are not
-changed often but are read a repeatedly a lot such as the information for subjects
-and their dependencies, user accounts, and recommended courses.
-
-\item Persistent Relational Database System - This will be used as the permanent
-storage for all data. The other two storage and database systems will synchronize
-to this database at specific intervals.
-\end{enumerate}
+In order to achieve its speed, Redis sacrifices data integrity by writing
+and reading all data to and from the main memory of the system. This leads to possible
+data loss upon the occurance of a power interruption while Redis hasn't yet synchronized
+its data to permanent storage. However, this should not matter as long as the server
+has proper uninterruptible power supply systems in place. Even if such an event occurs,
+Redis uses sequential writing which will simply cancel out the latest writes causing a
+rollback rather than corrupting the whole database.
 
@@
 
-The backend will be a server that serves a Representational State Transfer (REST)
+The backend is a server that serves a Representational State Transfer (REST)
 Application Programming Interface (API) through the Hypertext Transfer Protocol
@@
 backend will check for conflicts before executing the specified action. 
-To do this, a bitwise AND will be done on the current user's schedule and the
-schedule of the subject to be inserted. If the resulting value is not 0 then
-an error reply will be sent.
+In order to implement this, the students schedule is stored as a set of numbers
+that represent the index of each 15-minute block throughout the day beginning at
+7:00 AM. For example, the number represents the time from 7:00AM to 7:15AM. This
+representation is also applied to the schedule of each subject.
+
+With the said representation of schedules, conflict checking is done by simply executing
+a set intersection of the schedule of the student and the schedule of the subject. If the
+resulting set does not have the size of zero, then it can be said that there is a conflict
+between the two schedules.
 
@@
 
-The system will be designed to support HTTP Requests from specific domains
+The system is designed to support HTTP Requests from specific domains
 where the frontend code will be stored through the Access-Control-Allow-Origin header. 
-This is to be able to outsource the load added by frontend data being served as 
+This allows us to outsource the load added by frontend data being served as 
 it will take a significant amount of networking bandwidth to serve the images and
@@
 
-The frontend will be a static web application that fires REST requests to the
-backend server. The Javascript Object Notation (JSON) will be used to specify parameters
-for commands that require sending non-anonymous data while a normal GET request
-will be used for reading anonymous data. The frontend will also have an enlistment queue
-where the user can setup which subjects he/she would like to enlist and then
-send them as a batch to the server. This would lessen the number of connections
-that the server will receive lessening the number of threads running in the 
-backend.
+The frontend is a static web application that fires REST requests to the
+backend server. Requests use HTTP methods such as GET, POST, PUT, and DELETE to 
+specify how data on the server is specified. Some of the commands have the same URL
+but is executed by specifying the HTTP method. For example, a PUT request on the schedule
+URL enlists a subject while a DELETE request on the same URL will cancel a subject. the
+server will then respond with the result in Javascript Object Notation (JSON) format that
+includes the resulting data and the return code specifying the kind of error or if there is
+no error.
 
-The design for the frontend will try to follow Google's Material Design 
+A copy of the list of subjects and schedules in JSON format is also loaded with the backend
+making subject searching fast and reducing API server load by not sending requests that are known 
+to fail such as enlistment and waitlisting of already-conflicting subjects.
+
+The static file server of the frontend can be served on a server with a caching service
+like CloudFlare enabled which would cache the static web application into its own 
+Content Delivery Network(CDN).
+
+Moreover, the static web application can also be cached on the browser of the client by
+specifying Cache-Control headers. We can go even further by utilizing IndexDB, AppCache,
+and localStorage capabilities to store the frontend application which will completely store
+the application in the browser making it accessible even if the static server is down.
+
+This setup also lessens the number of connections that the server will receive lessening
+the number of threads running in the backend. This also alleviates the additional load 
+caused by students opening the site in multiple tabs and refreshing each tab repeatedly.
+
+The design for the frontend tries to follow Google's Material Design 
 Specification although not strictly. Along with this, it shall support mobile
@@
 
-The system shall be evaluated by its stability, efficiency, ease of use, and
-integration.
+The system is evaluated by its stability and efficiency.
 
-Its stability will be evaluated by running a fuzzer software on the different
-commands that the backend server accepts. If the fuzzer finds strings that 
-causes the backend to crash, show an error, or produce the wrong output then the
-system fails the stability test. If this happens, the errors shall be fixed and
-the system will again undergo the stability evaluation.
-
-The system's efficiency will be evaluated by running benchmarks on the system.
+The system's stability and efficiency were evaluated by running benchmarks on the system.
 Information such as requests per second, time per request, and transfer rate
-of each function will be collected. The system will also be tested if can 
+of each function are collected. The system was also be tested if it can 
 handle medium and heavy workloads by using load testing tools and services.
@@
 
-The system's ease of use will be evaluated through a survey along with additional
-criteria about other aspects of the system.
-The survey will be done with at least 500 respondents that will test the system
-and rate it under the following criteria:
-\begin{enumerate}
- \item the ability of the user-interface to be understandable without a manual;
- \item the way how buttons in the user-interface are positioned;
- \item the animations embedded into the user-interface
- \item the responsiveness of the system; and
- \item the additional features of the system.
-\end{enumerate}
+Benchmarks are run on both the API server and the database management system.
+
+The API server is benchmarked by running the tools wrk and apachebench. These two tools apply 
+load to the server by running thousands of connections and recording either the number
+of requests done after a certain duration or the time it takes for a specified number of requests to finish.
+
+On the other hand, the database management system is benchmarked by running its own benchmarking tool
+that can benchmark server-side scripts and simulate its interaction with a specified number of keys which
+makes the evaluation of the speed of a script when there are a certain number of data on the server much easier.
 
@@
 \begin{center}
-    \begin{tabular}{ | l | p{5cm} |}
+    \begin{tabular}[!htbp]{ | l | p{5cm} |}
     \hline
@@
 
+\section{Results and Discussion}
+\begin{tikzpicture}
+  \begin{axis}[ ybar, 
+		legend style={at={(0.5,-0.2)}, 
+		anchor=north,legend columns=-1}, 
+		ylabel={1000x Req/s}, 
+		symbolic x coords={Enlist, Cancel, Get Sched, Get Slots, Waitlist, Unwaitlist},
+		xtick=data, 
+		nodes near coords, 
+		nodes near coords align={vertical}, 
+		x tick label style={rotate=45,anchor=east}, ]
+		\addplot coordinates {(Enlist,65.5) (Cancel,49.0) (Get Sched,140.9) (Get Slots,102.3) (Waitlist,69.0) (Unwaitlist,73.7)};
+  \end{axis}
+\end{tikzpicture}
+\begin{center}
+  Figure 1. Database requests per second
+\end{center}
+\begin{tikzpicture}
+  \begin{axis}[ ybar, 
+		legend style={at={(0.5,-0.2)}, 
+		anchor=north,legend columns=-1}, 
+		ylabel={1000x Req/s}, 
+		symbolic x coords={Enlist, Cancel, Get Sched, Get Slots, Waitlist, Unwaitlist},
+		xtick=data, 
+		nodes near coords, 
+		nodes near coords align={vertical}, 
+		x tick label style={rotate=45,anchor=east}, ]
+		\addplot coordinates {(Enlist,18.1) (Cancel,17.7) (Get Sched,17.1) (Get Slots,17.6) (Waitlist,17.5) (Unwaitlist,17.7)};
+  \end{axis}
+\end{tikzpicture}
+\begin{center}
+  Figure 2. API server requests per second on a Dual Core i7-5600U
+\end{center}
+
+\section{Summary and Conclusion}
+
 % REFERENCES FORMAT
@@
 \bibliographystyle{sigchi}
-\bibliography{paper}
+\bibliography{sp2-paper}
 

### 2016-05-20 Paper/sp2-paper.tex
Pushed final paper

@@
-\documentclass[draft]{sigchi}
+\documentclass{sigchi}
 
@@
 
-Benchmarks are run on both the API server and the database management system.
+Benchmarks were ran on both the API server and the database management system.
 
@@
 
+In Figure 1, it is shown that the database management system, Redis, was able to serve an average of 83,400
+requests per second in an Intel Core i7-5600U. It should be noted that Redis is only able to utilize a single core
+so scaling through sharding will increase these numbers significantly.
+
+In Figure 2, it can be seen that the requests per second went down
+from the database average of 83,400 to 17,600 with low deviation on the same machine.
+This shows that the overhead caused by the API server is the bottleneck in this setup. 
+Early tests in the API server showed higher number of requests per second
+that can be blamed on the addition of URL parsers, data persistence middlewares, and JSON encoders
+that likely caused the reduction in the serving-speed. However, these benchmarks only shows its performance
+on a dual core system and the API server is highly multithreaded which implies that it could perform much faster
+on multicore and multiprocessor servers. Moreover, the API server can also be scaled by using a load balancer
+with it running on multiple servers that share the same database.
+
 \section{Summary and Conclusion}
 
+Based on the results of the system evaluation, we can conclude that the system is efficient enough to handle most 
+universities with large student 
+populations such as the University of the Philippines Los Baños that has around 13,710 students even if each student
+does an API requests once per second. It can be implied that it can also serve populations much larger than the benchmark
+results through scaling. 
 % REFERENCES FORMAT

### 2016-05-21 Paper/sp2-paper.tex
Add abstract

@@
 
-% \begin{abstract}
-% \end{abstract}
+\begin{abstract}
+One of the challenges of universities with high student populations in the Philippines is the implementation of
+an online enrollment system. Many of these systems were not tested to handle sudden heavy influx of user connections
+and the technologies used are not best-fitted for such occurence. In this research, we design and implement a system
+that can perform well under sudden surge of users by applying recent technological advances and design techniques. 
+We use Redis as the database for fast atomic database access, Rust as a language with Iron as the web server framework for faster 
+serving of HTTP requests by removing the need for a garbage collector, and the split client-server architecture that allows
+the offloading of heavy content to static servers. The implemented system is tested by running benchmarks on both the database and
+the server that will handle HTTP requests and measuring the number of requests per second. From this, we can see how it will perform
+during sudden heavy load that occur during the online registration period. The results proved the efficiency of the system by showing
+that it can serve an average of 17,600 requests per second with the database serving 83,400 requests per second on a dual-core system.
+Moreover, because the system is designed to be multithreaded and utilize all cores, the server should be able to linearly scale when
+more cores are added making it able to serve more than 50,000 requests on a higher-end computer. In the future, improvements in the Iron
+web server framework such as asynchronous IO, and faster parsing algorithms could further improve the server speed of the system
+as they are some of the bottlenecks of the system.
+\end{abstract}
 % 
@@
 % 
-\keywords{student; information; registration; enrollment}
+\keywords{student; information; registration; enrollment; Rust; Redis; static webapp}
 
@@
 
-\section{Timeline}
-\begin{center}
-    \begin{tabular}[!htbp]{ | l | p{5cm} |}
-    \hline
-      Date & Activity \\ \hline
-      Day 0-7 & Planning of System Framework and Database Structures \\ \hline
-      Day 8-14 & Implementation of Basic Backend Functions Without Conflict Checking \\ \hline
-      Day 15-30 & Implementation of Conflict Checking and Integration with Backend \\ \hline
-      Day 31-45 & Development of Static Web Application Interface \\ \hline
-      Day 46-60 & Implementation of Advanced Features \\ \hline
-      Day 61-68 & Stress Testing and Fuzzing \\ \hline
-      Day 69-76 & Adjustments from the Results of Stress Testing and Fuzzing \\ \hline
-      Day 77-81 & Alpha Test of Test Users \\ \hline
-      Day 82-96 & Adjustments from the Results of Alpha Test \\ \hline
-      Day 97-103 & Beta Release \\ \hline
-    \end{tabular}
-\end{center}
-
 \section{Results and Discussion}
@@
 \begin{center}
-  Figure 1. Database requests per second
+  Figure 1. Database requests per second on a Dual Core i7-5600U
 \end{center}

### 2016-05-22 HeartlandTester/main.js
rename directories and files

@@ -1,157 +1,0 @@
-var subjects = {}
-
-$.ajax({
-  url: 'subjects.json',
-  success: function(data) {
-    console.log(data)
-    subjects = data.subjects
-  }
-})
-
-function login() {
-  $.ajax({
-    type: 'POST',
-    url: 'http://localhost:3000/auth/login?username=' + $("#username").val() + '&password=' + $("#password").val(),
-    success: function(data) {
-      var res = JSON.parse(data);
-      if (res.key) {
-        $("#session").val(res.key);
-        Materialize.toast("Successfully logged in.", 1000);
-      } else {
-        Materialize.toast("Failed to logged in.", 1000);
-      }
-      console.log(res)
-    }
-  })
-  return false;
-}
-
-function logout() {
-  $.ajax({
-    type: 'POST',
-    url: 'http://localhost:3000/auth/logout?session=' + $("#session").val(),
-    success: function(data) {
-      var res = JSON.parse(data);
-      if (res.result == 0) {
-        $("#session").val('-');
-        Materialize.toast("Successfully logged out.", 1000);
-      } else {
-        Materialize.toast("Failed to logged out.", 1000);
-      }
-
-    }
-  })
-  return false
-}
-
-function get_profile() {
-  $.ajax({
-    type: 'GET',
-    url: 'http://localhost:3000/student/profile?session=' + $("#session").val(),
-    success: function(data) {
-      var res = JSON.parse(data);
-      $("#student_profile").html(
-        `<td>${res.data.student_number}</td>
-        <td>${res.data.first_name}</td>
-        <td>${res.data.middle_name}</td>
-        <td>${res.data.last_name}</td>
-        <td>${res.data.curriculum}</td>
-        <td>${res.data.standing}</td>
-        <td>${res.data.total_units}</td>
-        <td>${res.data.max_units}</td>`
-      )
-      console.log(res)
-    }
-  })
-  return false
-}
-
-function get_schedule() {
-  $.ajax({
-    type: 'GET',
-    url: 'http://localhost:3000/student/schedule?session=' + $("#session").val(),
-    success: function(data) {
-      var res = JSON.parse(data);
-      var html = ''
-
-      var c = initializeSched($("#schedule")[0]);
-
-      for (subject in res.data) {
-        var section = res.data[subject]
-        let subdata = subjects[subject][section]
[…]

### 2016-05-27 Paper/sp2-paper.tex
Minor fixes

@@
 an online enrollment system. Many of these systems were not tested to handle sudden heavy influx of user connections
-and the technologies used are not best-fitted for such occurence. In this research, we design and implement a system
-that can perform well under sudden surge of users by applying recent technological advances and design techniques. 
+and the technologies used are not best-fitted for such events. In this research, we design and implement a system
+that can perform well under sudden surges of users by applying the most recent technological advances and design techniques. 
 We use Redis as the database for fast atomic database access, Rust as a language with Iron as the web server framework for faster 
 serving of HTTP requests by removing the need for a garbage collector, and the split client-server architecture that allows
-the offloading of heavy content to static servers. The implemented system is tested by running benchmarks on both the database and
+the offloading of heavy content to static servers. The implemented system was tested by running benchmarks on both the database and
 the server that will handle HTTP requests and measuring the number of requests per second. From this, we can see how it will perform
@@
 
-The complexity of this process along with the increasing availability of Internet access to
-the public incited the development of computerized Online Registration Systems (ORS). These
-systems allowed the enlistment, cancellation, and swapping of slots for courses over the Internet.
-These systems also did the checking of conflicting subjects and availability of slots automatically
-so that students will not need to do them manually.
-In the University of the Philippines Los Baños (UPLB), the Online Registration System that
-is used as of the writing of this paper is called SystemOne. This system has undergone various
-revisions and improvements as old technology become deprecated by new ones and problems
-encountered in previous versions are fixed. The most recent one identifies itself as the third
-version and is code-named “Decaf”. However, this system did not prove to be efficient enough
-for the student population of UPLB despite several rewrites and revisions.
-This paper seeks to improve open this kind of online registration by fixing the problems encountered
-by SystemOne as a basis.
+The complexity of this process along with the increasing availability of Internet access to the public incited the development of computerized Online Registration Systems (ORS).
+These systems allowed the enlistment, cancellation, and swapping of slots for courses over the Internet.
+These systems also did the checking of conflicting subjects and availability of slots automatically so that students will not need to do them manually.
+In the University of the Philippines Los Baños (UPLB), the Online Registration System that is used as of the writing of this paper is called SystemOne.
+This system has undergone various revisions and improvements as old technology become deprecated by new ones and problems encountered in previous versions are fixed.
+The most recent one identifies itself as the third version and is code-named “Decaf”.
+However, this system did not prove to be efficient enough for the student population of UPLB despite several rewrites and revisions.
+This paper seeks to improve open this kind of online registration by fixing the problems encountered by SystemOne as a basis.
 
@@
 
-There is a limited number of papers that specifically discuss SystemOne. These papers
-mostly focus on the various modules that provide different kinds of functionality for SystemOne
-and the features to be created rather than the speed and feasibility of the use of the system.
-Suayan (1997) developed one of the first registration systems used in UPLB called the
-UPLB RegisNet \cite{suayan}. This system was designed to automate the pre-enlistment of subjects for
-students.
+There is a limited number of papers that specifically discuss SystemOne.
+These papers mostly focus on the various modules that provide different kinds of functionality for SystemOne and the features to be created rather than the speed and feasibility of the use of the system.
+Suayan (1997) developed one of the first registration systems used in UPLB called the UPLB RegisNet \cite{suayan}.
+This system was designed to automate the pre-enlistment of subjects for students.
 
-Meanwhile, the UPLB Academic Information System was created and had support for
-modularity. Through its modularity, various modules were created for it. Cruz (2001) created a
-Subjects module that gave it the ability to add, edit, and delete subjects from a list of subjects \cite{cruz} and
-Almodiel (2001) developed a module that allowed teachers to add, search, and view the grades of
-a student in their respective classes \cite{almodiel}. Enrique (2001) then developed a Schedule of Classes
-module that was responsible for managing and viewing the schedule of a subject, a room, or a
-teacher \cite{enrique}.
+Meanwhile, the UPLB Academic Information System was created and had support for modularity.
+Through its modularity, various modules were created for it.
+Cruz (2001) created a Subjects module that gave it the ability to add, edit, and delete subjects from a list of subjects \cite{cruz} and Almodiel (2001) developed a module that allowed teachers to add, search, and view the grades of a student in their respective classes \cite{almodiel}.
+Enrique (2001) then developed a Schedule of Classes module that was responsible for managing and viewing the schedule of a subject, a room, or a teacher \cite{enrique}.
 
-After a few years, Javier, et al. (2005) developed the first version of UPLB’s Online
-Registration System called SystemOne \cite{javier}. This system was also extensible through modularity. In
-this version, SystemOne used the Java programming language for implementing the Enlistor and
-Registrar module, PHP 5 for the Department module and MySQL as the Database Management
-System (DBMS).
+After a few years, Javier, et al.
+(2005) developed the first version of UPLB’s Online Registration System called SystemOne \cite{javier}.
+This system was also extensible through modularity.
+In this version, SystemOne used the Java programming language for implementing the Enlistor and Registrar module, PHP 5 for the Department module and MySQL as the Database Management System (DBMS).
 
-In 2010, the development of the UPLB SystemOne V2 began. This version also
-used the Java programming language and the MySQL DBMS and was also modular. However,
-the difference of this new system from the previous system was that even the core functions were
-divided into modules and was developed separately.
+In 2010, the development of the UPLB SystemOne V2 began.
+This version also used the Java programming language and the MySQL DBMS and was also modular.
+However, the difference of this new system from the previous system was that even the core functions were divided into modules and was developed separately.
 
-In 2012, the third and current version of SystemOne was developed by the SystemOne
-Development Team. This system, unlike the previous versions that used Java, used the PHP
-programming language along with the MySQL DBMS. Like the second version, this system
-supports modules and its core functions are also implemented as modules.
+In 2012, the third and current version of SystemOne was developed by the SystemOne Development Team.
+This system, unlike the previous versions that used Java, used the PHP programming language along with the MySQL DBMS.
+Like the second version, this system supports modules and its core functions are also implemented as modules.
 
-There was one study that focused on the speed and response time of SystemOne. Crespo
-(2014) wrote a study entitled “Comparing the Response and Rendering Time of PHP-based
-against Javascript-based SystemOne” \cite{crespo}. This study did a comparison on how much faster or slower
-SystemOne would be had it been implemented in Javascript using the NodeJS interpreter. Her
-study detailed the performance of her own Javascript-based implementation against the
-PHP-based implementation. The results of her study showed that the Javascript-based
-implementation yielded a 52 percent increase in overall speed.
+There was one study that focused on the speed and response time of SystemOne.
+Crespo (2014) wrote a study entitled “Comparing the Response and Rendering Time of PHP-based against Javascript-based SystemOne” \cite{crespo}.
+This study did a comparison on how much faster or slower SystemOne would be had it been implemented in Javascript using the NodeJS interpreter.
+Her study detailed the performance of her own Javascript-based implementation against the PHP-based implementation.
+The results of her study showed that the Javascript-based implementation yielded a 52 percent increase in overall speed.
 
-These results seem to be very promising considering the fact that NodeJS is known to not be
-able to take full advantage of a server computer that has multiple cores yet. This shows that
-SystemOne could have been faster if the right choices were made.
-These studies show a history of Online Registration Systems used in UPLB. It can be seen in
-the papers and articles cited that the use of the best and fastest technology has not really been
-given consideration.
+These results seem to be very promising considering the fact that NodeJS is known to not be able to take full advantage of a server computer that has multiple cores yet.
+This shows that SystemOne could have been faster if the right choices were made.
+These studies show a history of Online Registration Systems used in UPLB.
+It can be seen in the papers and articles cited that the use of the best and fastest technology has not really been given consideration.
 
@@
 
-As an information system, the speed of the system depends heavily on the speed
-of the database management system since most of the requests that it handles
-do modification of data. Because of this, Redis was chosen as it is a database
-management system that has low runtime overhead and very fast request-serving
-speeds with benchmarks showing hundreds of thousands of requests per second for
-atomic functions.
+As an information system, the speed of the system depends heavily on the speed of the database management system since most of the requests that it handles do modification of data.
+Because of this, Redis was chosen as it is a database management system that has low runtime overhead and very fast request-serving speeds with benchmarks showing hundreds of thousands of requests per second for atomic functions.
 
-In order to achieve its speed, Redis sacrifices data integrity by writing
-and reading all data to and from the main memory of the system. This leads to possible
-data loss upon the occurance of a power interruption while Redis hasn't yet synchronized
-its data to permanent storage. However, this should not matter as long as the server
-has proper uninterruptible power supply systems in place. Even if such an event occurs,
-Redis uses sequential writing which will simply cancel out the latest writes causing a
-rollback rather than corrupting the whole database.
+In order to achieve its speed, Redis sacrifices data integrity by writing and reading all data to and from the main memory of the system.
+This leads to possible data loss upon the occurance of a power interruption while Redis hasn't yet synchronized its data to permanent storage.
+However, this should not matter as long as the server has proper uninterruptible power supply systems in place.
+Even if such an event occurs, Redis uses sequential writing which will simply cancel out the latest writes causing a rollback rather than corrupting the whole database.
 
@@
 
-The backend is a server that serves a Representational State Transfer (REST)
-Application Programming Interface (API) through the Hypertext Transfer Protocol
-(HTTP). The system's backend shall have multithreading support. A thread will be 
-spawned for every successful HTTP connection. This thread will handle its own
-associated connection and wait for a command before processing it and giving a 
-reply. If a command is not received or completed after a specified amount of
-time, a timeout will occur and the connection will be dropped along with its
-corresponding thread being deallocated from the memory.
+The backend is a server that serves a Representational State Transfer (REST) Application Programming Interface (API) through the Hypertext Transfer Protocol (HTTP).
+The implementation of the backend utilizes multithreading in order to be able to use all processor cores for the processing of HTTP requests.
+A thread will be spawned for every successful HTTP connection.
+This thread will handle its own associated connection and wait for a command before processing it and giving a reply.
+If a command is not received or completed after a specified amount of time, a timeout will occur and the connection will be dropped along with its corresponding thread being deallocated from the memory.
 
@@
 
-Every time a modification or addition is done on a student's schedule, the 
-backend will check for conflicts before executing the specified action. 
-In order to implement this, the students schedule is stored as a set of numbers
-that represent the index of each 15-minute block throughout the day beginning at
-7:00 AM. For example, the number represents the time from 7:00AM to 7:15AM. This
-representation is also applied to the schedule of each subject.
+Every time a modification or addition is done on the schedule of a student, the backend will check for conflicts before executing the specified action.
+In order to implement this, the students schedule is stored as a set of numbers that represent the index of each 15-minute block throughout the day beginning at 7:00 AM.
+For example, the number represents the time from 7:00AM to 7:15AM.
+This representation is also applied to the schedule of each subject.
 
-With the said representation of schedules, conflict checking is done by simply executing
-a set intersection of the schedule of the student and the schedule of the subject. If the
-resulting set does not have the size of zero, then it can be said that there is a conflict
-between the two schedules.
+With the said representation of schedules, conflict checking is done by simply executing a set intersection of the schedule of the student and the schedule of the subject.
+If the resulting set does not have the size of zero, then it can be said that there is a conflict between the two schedules.
 
@@
 
-Moreover, the static web application can also be cached on the browser of the client by
-specifying Cache-Control headers. We can go even further by utilizing IndexDB, AppCache,
-and localStorage capabilities to store the frontend application which will completely store
-the application in the browser making it accessible even if the static server is down.
+Moreover, the static web application can also be cached on the browser of the client by specifying Cache-Control headers.
+We can go even further by utilizing IndexDB, AppCache, and localStorage capabilities to store the frontend application which will completely store the application in the browser making it accessible even if the static server is down.
 
-This setup also lessens the number of connections that the server will receive lessening
-the number of threads running in the backend. This also alleviates the additional load 
-caused by students opening the site in multiple tabs and refreshing each tab repeatedly.
+This setup also lessens the number of connections that the server will receive lessening the number of threads running in the backend.
+This also alleviates the additional load caused by students opening the site in multiple tabs and refreshing each tab repeatedly.
 
-The design for the frontend tries to follow Google's Material Design 
-Specification although not strictly. Along with this, it shall support mobile
-platforms by implementing Responsive Design.
+The design for the frontend tries to follow Material Design Specification by Google although not strictly. Along with this, it shall support mobile platforms by implementing Responsive Design.
 
@@
 
-The system's stability and efficiency were evaluated by running benchmarks on the system.
-Information such as requests per second, time per request, and transfer rate
-of each function are collected. The system was also be tested if it can 
-handle medium and heavy workloads by using load testing tools and services.
-These tests will use combinations of the different functions at ratios expected
-during actual use of the system.
+The stability and efficiency of the system were evaluated by running benchmarks on the system.
+Information such as requests per second, time per request, and transfer rate of each function are collected.
+The system was also be tested if it can handle medium and heavy workloads by using load testing tools and services.
+These tests will use combinations of the different functions at ratios expected during actual use of the system.
 
 Benchmarks were ran on both the API server and the database management system.
+The API server is benchmarked by running the tools wrk and apachebench.
+These two tools apply load to the server by running thousands of connections and recording either the number of requests done after a certain duration or the time it takes for a specified number of requests to finish.
 
-The API server is benchmarked by running the tools wrk and apachebench. These two tools apply 
-load to the server by running thousands of connections and recording either the number
-of requests done after a certain duration or the time it takes for a specified number of requests to finish.
-
-On the other hand, the database management system is benchmarked by running its own benchmarking tool
-that can benchmark server-side scripts and simulate its interaction with a specified number of keys which
-makes the evaluation of the speed of a script when there are a certain number of data on the server much easier.
+On the other hand, the database management system is benchmarked by running its own benchmarking tool that can benchmark server-side scripts and simulate its interaction with a specified number of keys which makes the evaluation of the speed of a script when there are a certain number of data on the server much easier.
 
@@
 
-In Figure 1, it is shown that the database management system, Redis, was able to serve an average of 83,400
-requests per second in an Intel Core i7-5600U. It should be noted that Redis is only able to utilize a single core
-so scaling through sharding will increase these numbers significantly.
+In Figure 1, it is shown that the database management system, Redis, was able to serve an average of 83,400 requests per second on an Intel Core i7-5600U.
+It should be noted that Redis is only able to utilize a single core so scaling through sharding will linearly increase this serving speed.
 
-In Figure 2, it can be seen that the requests per second went down
-from the database average of 83,400 to 17,600 with low deviation on the same machine.
+It is also noted that the command for retrieving the schedule is processed the fastest at 140,900 requests per second.
+This is because it is the least complex command that consists only of a single read request to the database after input validation.
+On the other hand, it can be seen that the command for cancellation of subjects is processed the slowest.
+This is due to it being the most complex command involving input validation, retrieval and verification of enlisted subject, actuall removal of enlisted subject, retrieval of the front element in the waitlist queue, conflict checking of subject against the schedule of the waitlister, and, finally, the enlistment of the waitlister.
+
+In Figure 2, it can be seen that the requests per second went down from the database average of 83,400 to 17,600 with low deviation on the same machine.
 This shows that the overhead caused by the API server is the bottleneck in this setup.
-Early tests in the API server showed higher number of requests per second
-that can be blamed on the addition of URL parsers, data persistence middlewares, and JSON encoders
-that likely caused the reduction in the serving-speed. However, these benchmarks only shows its performance
-on a dual core system and the API server is highly multithreaded which implies that it could perform much faster
-on multicore and multiprocessor servers. Moreover, the API server can also be scaled by using a load balancer
-with it running on multiple servers that share the same database.
+Early tests in the API server showed higher number of requests per second that can be blamed on the addition of URL parsers, data persistence middlewares, and JSON encoders that likely caused the reduction in the serving-speed.
+However, these benchmarks only shows its performance on a dual core system and the API server is highly multithreaded which implies that it could perform much faster on multicore and multiprocessor servers.
+Moreover, the API server can also be scaled by using a load balancer with it running on multiple servers that share the same database.
 
@@
 
-Based on the results of the system evaluation, we can conclude that the system is efficient enough to handle most 
-universities with large student 
-populations such as the University of the Philippines Los Baños that has around 13,710 students even if each student
-does an API requests once per second. It can be implied that it can also serve populations much larger than the benchmark
-results through scaling. 
+Based on the results of the system evaluation, we can conclude that the system is efficient enough to handle most universities with large student populations such as the University of the Philippines Los Baños that has around 13,710 students even if each student does an API requests once per second.
+It can be implied that it can also serve populations much larger than the benchmark results through scaling.
 % REFERENCES FORMAT
